A linearization procedure for constrained multibody systems

### 2012-03-31 PetersonGedeHubbard2012.tex
Worked on discussion section, added a reference.

The first three equations in table \ref{table:assumptions} represent

@@

\section{Derivation of linearization algorithm}
\label{derivations}

We see in Table \ref{table:assumptions} the differential equations which
describe our system. The goal of this procedure is to create linear equations
of motion with the following structure:
\begin{align}
    \label{eq:structure}
    \tilde{M} \dot{\bm{x}} = \tilde{A} \bm{x}_i + \tilde{B} \bm{r}
\end{align}
where $\bm{x}$ is the state vector of all the coordinates and speeds and
$\bm{x}_i$ is the state vector of only the independent coordinates and speeds.
From this equation we can perform numerical integration or stability analysis,
or it can be reformulated into the traditional state space equations for
controller design.

@@

We now have a linear system of equations which relates the time derivatives of all
states, dependent or independent, to the independent coordinates, independent
speeds, and exogenous inputs.

\section{Discussion}

There are a number of additional steps needed to use these linear equations or
form them more efficiently. There are also non-singularity requirements
involved in selection of independent quantities.

In order to use these equations in the state space representation, 2 things
need to happen. First, matrices $\tilde{A}$ and $\tilde{B}$ need to be
multiplied by the mass matrix inverse. We can then define

\begin{align}
    A^\prime &\triangleq \tilde{M}^{-1} \tilde{A} \\
    B^\prime &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}

Now we will have matrices $A^\prime$ and $B^\prime$ which are of size $(o +
n) \times (o - m + n - l)$ and $(o + n) \times p)$. We need to now extract only
the rows which are associated with the independent quantities. We will call the
new reduced matrices $A$ and $B$ and compute them with the following

\begin{align}
    P^\prime &\triangleq \begin{bmatrix}
        P_{qi} & \bm{O}_{n \times (o - m)} \\
        \bm{O}_{o \times (n - l)} & P_{ui}
    \end{bmatrix} \\
    A &\triangleq P^{\prime T} A^\prime \\
    B &\triangleq P^{\prime T} B^\prime
\end{align}

We will also define the state space vector $x =
\left[\delta\bm{q}_i,\,\delta\bm{u}_i\right]^{T}$; we now have the traditional
state space representation which only contains independent quantities.

This method relies on the nonsingularity of $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$
and $\nabla_{\bm{u}} \bm{f}_{v} P_{ud}$.  The implication of this is that
selection of dependent coordinates and dependent speeds is critical.  The
permutation matrices effectively select the columns of the constraint gradient
matrices, and may be selected by examination of the constraint gradient matrix
through a SVD or other numerical techniques; for small systems it may be
possible to choose dependent speeds without resorting to numerical techniques
if the system trajectories stay with the configuration space where these
matrices are nonsingular.

>>>>

The first three equations in Table \ref{table:assumptions} represent

@@

\section{Derivation of linearization algorithm}
\label{sec:derivations}

We see in Table \ref{table:assumptions} the differential equations which
describe our system. The goal of this section is to create linear equations
of motion with the following structure:
\begin{align}
    \label{eq:structure}
    \tilde{M} \dot{\bm{x}} = \tilde{A} \bm{x}_i + \tilde{B} \bm{r}
\end{align}
where $\bm{x}$ is the state vector of all the coordinates and speeds and
$\bm{x}_i$ is the state vector of only the independent coordinates and speeds.
This equation can be used for simulation, stability analysis,
or it can be reformulated into the traditional state space equations for
controller design; these topics are discussed in \ref{sec:discussion}

@@

We now have a linear system of equations which relates the time derivatives of all
states (dependent and independent) to the independent states and exogenous inputs.

\section{Discussion}
\label{sec:discussion}
Equation \ref{eq:state_space_constrained} doesn't fit into the standard linear
system framework because it is non-square.  To obtain a square system (useful
in stability analysis and control system design) we define
\begin{align}
    A^\prime &\triangleq \tilde{M}^{-1} \tilde{A} \\
    B^\prime &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}
where  $A^\prime \in \bm{R}^{(o + n) \times (o - m + n -l)}$, $B^\prime \in
\bm{R}^{(o + n) \times p)}$.  We can extract the rows corresponding to the
independent states by defining
\begin{align}
    P^\prime &\triangleq \begin{bmatrix}
        P_{qi} & \bm{O}_{n \times (o - m)} \\
        \bm{O}_{o \times (n - l)} & P_{ui}
    \end{bmatrix} \\
    A &\triangleq P^{\prime T} A^\prime \\
    B &\triangleq P^{\prime T} B^\prime
\end{align}
where $P^\prime \in \bm{R}^{(o - m + n - l) \times (o - m + n - l)}$.  Defining
$\bm{x}_i = \left[\delta\bm{q}_i,\,\delta\bm{u}_i\right]^{T}$ yields the square
state space system $\dot{\bm{x}}_i = A \bm{x}_i + B \bm{r}$.  The standard
linear systems analyses may now be applied.  It is worth noting that the rows
of $A^\prime$ and $B^\prime$ which correspond to dependent states can be used
in the output or measurement equations of a linear state space model, as would
be the case when the control task is to control a dependent state or when
measurements of dependent state(s) are made.

The choice on which state variables are taken to be independent may determine
whether $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$ and $\nabla_{\bm{u}} \bm{f}_{v}
P_{ud}$ are nonsingular.  These matrices depend upon the
configuration variables and parameters; for certain configurations or
parameters, it may be that the choice of independent state variables cannot be
arbitrary.  While some systems may permit a choice of independent state
variables which are valid for all configurations of interest, others may not.
Methods for automatically selecting the ``best'' choice of independent state
variables are discussed in \cite{Reckdahl1996}; they involve computing
the SVD of the Jacobian of the constraint matrices to determine a set of
indepedent speeds which will ensure the nonsingularity of the aforementioned
matrices.
